The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-11-01 ms.Rmd
re-organising Figure 2

```{r fengChangeWorkflow, eval = TRUE, fig.show = "hide", fig.height = 9}
FengPapesUpdate <- 
  ChangeWorkflow(workflow = FengPapes,
                   output = Chain(InteractiveMap, 
                                  ResponseCurve(cov = 1)))
```

```{r combinefengupdate, eval = TRUE, echo = FALSE, dpi = 600, fig.show = "hide", fig.height = 3.2}
# combine the static and interactive maps and first effect plot

@@

# set up layout so that heights are the same for both panels
plot_height <- min(nrow(r_map1), nrow(r_map), nrow(r_resp))

@@

# set up layout (maximum total of 200 columns) with a gap in between
# mar won't work for these
gap <- 2
widths <- c(width_map1, width_map, width_resp)
widths <- round(widths * ((200 - (2 * gap)) / sum(widths)))
widths <- c(widths[1], gap, widths[2], gap, widths[3])
mat <- matrix(rep(1:5, widths),
              nrow = 1)
layout(mat)

# plot statis map
plotRGB(r_map1, maxpixels = Inf)

# add a panel letter
mtext(text = 'A',
        side = 3,
        line = -3,
        adj = 0)

@@

# add a panel letter
mtext(text = 'B',
        side = 3,
        line = -3,
        adj = 0)

# add a panel letter
mtext(text = 'C',
        side = 3,
        line = -3,
        adj = 0)

@@

```{r feng_papes_plots, cache = FALSE, echo = FALSE, out.width = "450px", fig.cap = "Outputs of the workflow objects `FengPapes' and `FengPapesUpdate'. A) Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence generated by the `PrintMap' module in the workflow `FengPapes'. White areas are masked due to being in the sea or outside the MESS mask. B) A screenshot of the interactive map produced by the `InteractiveMap' modules in the workflow `FengPapesUpdate', displaying raw occurrence data and predicted distribution over a global map, allowing users to interactively explore their results. C) A response curve produced by the `ResponseCurve' module for the first covariate, bio1 in the workflow `FengPapesUpdate'."}
knitr::include_graphics("figs/combinefengupdate-1.png")
```

>>>>

```{r fengChangeWorkflow, eval = TRUE, fig.show = "hide", fig.height = 9}
FengPapesUpdate <- 
  ChangeWorkflow(workflow = FengPapes,
                   output = Chain(ResponseCurve(cov = 1),
                                  InteractiveMap))
```

```{r combinefengupdate, eval = TRUE, echo = FALSE, dpi = 600, fig.show = "hide", fig.height = 4.5, fig.width = 4.5}
# combine the static and interactive maps and first effect plot

@@

# set up layout so that heights are the same for all panels
plot_height <- min(nrow(r_map1), nrow(r_map), nrow(r_resp))

@@

# set up layout (maximum total of 200 columns) with a gap in between
# mar won't work for these
gap <- 2

# top row: map1 and resp
widths_top <- c(width_map1, width_resp)
widths_top <- round(widths_top * ((200 - (1 * gap)) / sum(widths_top)))
widths_top <- c(widths_top[1], gap, widths_top[2])

top_row <- rep(1:3, widths_top)
bottom_row <- rep(5, length(top_row))

heights <- c(plot_height + 1, plot_height)
heights <- round(heights * ((50 - (1)) / sum(heights)))
heights <- c(heights[1], 1, heights[2])

top_matrix <- do.call(rbind, replicate(heights[1], top_row, simplify = FALSE))
middle_matrix <- matrix(4, nrow = heights[2], ncol = ncol(top_matrix))
bottom_matrix <- matrix(5, nrow = heights[3], ncol = ncol(top_matrix))

mat <- rbind(top_matrix, middle_matrix, bottom_matrix)
layout(mat)

# plot static map
plotRGB(r_map1, maxpixels = Inf)

# add a panel letter
mtext(text = 'A',
        side = 3,
        line = -1.5,
        adj = 0)

# add a panel letter
mtext(text = 'B',
        side = 3,
        line = -1.5,
        adj = 0)

@@

# add a panel letter
mtext(text = 'C',
        side = 3,
        line = -1.5,
        adj = 0)

@@

```{r feng_papes_plots, cache = FALSE, echo = FALSE, out.width = "450px", fig.cap = "Outputs of the workflow objects `FengPapes' and `FengPapesUpdate'. A) Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence generated by the `PrintMap' module in the workflow `FengPapes'. White areas are masked due to being in the sea or outside the MESS mask. B) A response curve produced by the `ResponseCurve' module for the first covariate, bio1 in the workflow `FengPapesUpdate'. C) A screenshot of the interactive map produced by the `InteractiveMap' modules in the workflow `FengPapesUpdate', displaying raw occurrence data and predicted distribution over a global map, allowing users to interactively explore their results."}
knitr::include_graphics("figs/combinefengupdate-1.png")
```
